\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
replace enumeration, it's out of place

Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and potentially 
programmatically if it must be performed for large numbers of objects. The processes include; 
\begin{enumerate}
\item merging registries, 
\item removing volumes (de-featuring),
\item editing solid parameters,
\item replacing logical volume materials 
\item converting logical volumes to assembly volumes.
\end{enumerate}
The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
Each sub-component is stored in a separate registry and these have to combined without any GDML tags clashing. 
The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be 
safely removed. Examples of other workflows or geometry manipulation processes can be found in 
the \PYGEOMETRY{} online manual.

>>>>

Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and programmatically. The benefits of the API are
particularly apparent when needing to process large amounts of geometry efficiently and precisesly. Possible transformations include merging registries, 
removing volumes (de-featuring), editing solid parameters, changing logical volume materials and converting logical volumes to assembly volumes.

The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
Each sub-component is stored in a separate registry and these have to combined without any GDML tags clashing. 
The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be 
safely removed. Examples of other workflows or geometry manipulation processes can be found in 
the \PYGEOMETRY{} online manual.
